\hypertarget{index_Introduction}{}\section{Introduction}\label{index_Introduction}
My name is Michel Baartman and I wrote these libraries to create custom dice that would be able to roll any number and are lightweight enough to fit on smaller arduino models. The entire idea behind this project was to create custom dice that would be able to roll any number and have a library lightweight enough to fit onto smaller Arduino models for a pocketsize (truly) custom dice. I also wanted to create a dice that would give feedback back to the user in sound as well, so that blind people might enjoy dice a bit more. I want to give a shoutout to Dylan Rakiman for figuring out how to wake the gyroscope up. If you are having issues waking up the gyroscope, try checking if the mpu\+\_\+addr in \hyperlink{classgyro__mpu6050}{gyro\+\_\+mpu6050} is the right one by running the i2c scanner by Nick Gammon\+: \href{http://www.gammon.com.au/forum/?id=10896,}{\tt http\+://www.\+gammon.\+com.\+au/forum/?id=10896,} the default address is 0x68. Be warned though\+: so far it has only been tested on an Arduino D\+UE and is not nearly as leightweight as I want it to be.\hypertarget{index_gyro_mpu6050}{}\section{gyro\+\_\+mpu6050}\label{index_gyro_mpu6050}
This (hardware focused) library will allow you to wake up your mpu6050 controller, which is always asleep on startup, and extract raw data from it.\hypertarget{index_gyro_dice}{}\section{gyro\+\_\+dice}\label{index_gyro_dice}
This (software focused) library will use and work with the data given from the \hyperlink{classgyro__mpu6050}{gyro\+\_\+mpu6050} library, making it usable and turning its data into a dice-\/like simulation. \hypertarget{index_gyro_dice_d6}{}\subsection{gyro\+\_\+dice\+\_\+d6}\label{index_gyro_dice_d6}
Simulates a 6 sided dice. So far uses fixed gyroscope values but I am working on a calibration function. \hypertarget{_}{}\subsection{}\label{_}
Simulates a 20 sided dice. N\+YI \hypertarget{index_gyro_dice_d0}{}\subsection{gyro\+\_\+dice\+\_\+d0}\label{index_gyro_dice_d0}
Simulates a random number generator dice. Checks wether the dice is shaking or not and once its halted prints a random number on the display. \hypertarget{index_gyro_dice_m8}{}\subsection{gyro\+\_\+dice\+\_\+m8}\label{index_gyro_dice_m8}
Simulates a magic 8 ball. C\+Hecks wether the dice is shaking or not and prints a random answer out of 22 possible answers.\hypertarget{index_dependencies}{}\section{dependencies}\label{index_dependencies}
These libraries are dependant on the H\+W\+L\+IB library which is required to manipulate the pins to our bidding. 